Describing the C-space of asynchronous periodic task using DIT

### 2013-07-22 dit-paper_ieee.tex
Added section on CSPACE asynchr

@@

\section{Description of the C-space of asynchronous system}
  \label{sct:asyncCspace}

>>>>

  \label{sct:cspaceDescr}

@@

\section{C-space of asynchronous systems}
  \label{sct:asyncCspace}

  \subsection{Description using DBF}

  The description we presented in Section \ref{sct:cspaceDescr} was general, and is thus still relevant: $$\sum_{i=0}^{n-1} n_i(t_1, t_2) \, C_i \leq t_2 - t_1 \; \forall \: 0 \leq t_1 \leq t_2$$

  The method used to remove redundancy, however, assumed the synchronous case. A more general approach is presented in the following section.

\subsubsection{Job arrival and deadline}

Consider an interval $[t_1, t_2]$. If $t_2$ is an instant without any job deadline, then by definition the value of $\dbf{t_1, t_2}$ will be equal to $\dbf{t_1, t_2^*}$, where $t_2^*$ is the latest deadline before $t_2$.\\

A similar argument can be made if $t_1$ is an instant without any job arrival (and $t_1^*$ is the earliest arrival after $t_1$). We can thus restricts ourselves to intervals where $t_1$ is an instant with at least one job arrival, and $t_2$ is an instant with at least one job deadline.

  \subsubsection{Feasibility interval}

  First let us recall how an asynchronous system behaves under, for example, EDF.\\

\begin{figure}[h]
$$
\begin{array}{|c|c|c|c|l}
   \text{Incomplete} & \text{Transitive} & \text{Stationary} & \text{$2^{nd}$ Stationary} & \cdots \\
   \text{period} & \text{period} & \text{period} & \text{period} & \\
  \hline
  t > 0 & O_{max} & O_{max} + H & O_{max} + 2H & \cdots
\end{array}
$$
\begin{center}
\caption{Behavior of an asynchronous system under EDF.}
\label{fig:asyncBehavior}
\end{center}
\end{figure}

As shown in Fig. \ref{fig:asyncBehavior}, the system begins in the \emph{incomplete period}, where all tasks are not in the system. Then, after $O_{max}$ time units, every tasks is in the system and the \emph{transitive period} begins. Then, after $O_{max} + H$ time units, the system is faced with the same pattern of arrival as in $O_{max}$. However, because in $O_{max} + H$ every task is in the system and in $O_{max}$ some were missing, the state of the system will be different. The \emph{stationary period} then begins. It is only after $O_{max} + 2H$ time units that the system comes back into a state in which it was before.\\

For this reason, as explained in \cite{leung1982complexity}, it is sufficient to check for intervals included in the interval $[O_{max}, O_{max} + 2H]$, which has an exponential length in the number of tasks.

\subsubsection{Using the first periodic DIT}

The first periodic DIT happen...
